\documentclass[a4paper, 11pt]{article}
\usepackage[top=2cm, bottom=3cm, left = 2cm, right = 2cm]{geometry} 
\geometry{a4paper} 
\usepackage{textcomp}
\usepackage{graphicx} 
\usepackage{amsmath,amssymb}  
\usepackage{bm}  
\usepackage{memhfixc} 
\usepackage{fancyhdr}
\usepackage{enumerate}
\usepackage{float}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{mathtools}
\pagestyle{fancy}
\setlength{\headheight}{14pt}
\addtolength{\topmargin}{-2pt}

\title{Advanced Network Security: Assignment \#2}
\author{Hossein Afkar \\ 810101102}
%\date{}

\begin{document}
\maketitle
% \tableofcontents
\section{Q1}
Because of definition of $\equiv$ we have $a \equiv b (mod) c$: that
$\forall d \in Z$ we have $a = dc + b$
For $H(m) \equiv xr + sk (mod p - 1)$ we can also find a d that:
\begin{equation}
    H(m) = xr + sk + (p-1)d
\end{equation}
Fermat's little theorem that we had from previous assignment proves that
for $p$ and $g \stackrel{p}{\equiv} 0$ we have
$g^{p-1} \stackrel{p}{\equiv} 1$.
Using that we can formally prove the signature scheme. From the signature
generation in ElFamal we can derive that:
\begin{equation}
    g^{H(m)} \equiv g^{xr + sk + (p-1)d}
\end{equation}
Fermat's little theorem can be used here to eliminate $(g^{p-1})^d$
\begin{equation}
    \equiv (g^{x})^{r} (g^{k})^s (g^{p-1})^{d}
\end{equation}
\begin{equation}
    \equiv (g^{x})^{r} (g^{k})^s 1^d
\end{equation}
\begin{equation}
    \equiv (g^{x})^{r} (g^{k})^s
\end{equation}
\begin{equation}
    \equiv y^{r} r^s
\end{equation}
\section{Q2}
For RSA we have to choose two prime numbers $p$ and $q$
and then compute the $n = pq$. After picking an encryption key $e \in
Z_{n^\prime}$ we have message as $m: c = m^e$ and decryption as $c: m = c^d$.
\\
Our thesis is:
\begin{equation}
    (m^e)^d \stackrel{n}{\equiv} m, \text{ for all } m \in Z_{n}
\end{equation}
Chinese remainder thereom states that if $gcd(p,q)=1$.
\begin{equation}
    x = y \pmod p \land x = y \pmod q \Rightarrow x = y \pmod{pq}
\end{equation}
So if can prove that the following two statements are correct we have proved
the theorem:
\begin{equation}
    (m^e)^d = m \mod p
\end{equation}
\begin{equation}
    (m^e)^d = m \mod q
\end{equation}
Because $gcd(m,n) \neq 1$, one of $gcd(m,n) = p$ or $gcd(m,n) = q$ must be
true. we start with $gcd(m,n) = p$. \\
So if $gcd(m,n) = p$ then we have $m = kp$ which measns that $m \mod p = 0$.
\begin{equation}
    (m^e)^d = ((kp)^e)^d
\end{equation}
So equation (9) is proved to be correct.
For equation (10) we have the following as stated in fermat's little theorem:
\begin{equation}
    m^{q-1} = 1 \mod q
\end{equation}
So using this we can continue with (10).
\begin{equation}
    \begin{aligned}
        (m^{e})^d &= m^{ed} \\
                  &= m^{ed - 1}m\\
                  &= m^{h(p-1)(q-1)}m\\
                  &= (m^{q-1})^{h(p-1)}m\\
                  &= 1^{h(p-1)}m = m \bmod{q}.
    \end{aligned}
\end{equation}
Which prooves that the second equation and therefore our whole theorem is
correct and RSA works when $gcd(m,n) \neq 1$.
\section{Q3}
\subsection{a}
False-accept happens when the user does not have the required privilages but
is granted access to the resource. \\
Flase-reject happens when the user does have access to the required privilages
but is denied access to the resource.
\subsection{b}
So we need the probability of the false-reject to happen at least 5 times.
\begin{equation}
    p(\text{false-reject } \times 5) = (0.1) ^ 5
\end{equation}
\subsection{c}
So if we get access the first time the probability is 0.005 or 0.5\%.
For the second time we need to be rejected first and get access in the second
try.
\begin{equation}
    p(\text{false-accept in second try}) = (1 - 0.005) \times 0.005 = 0.004975
\end{equation}
So the probability decreases for the second time. For the third time we have.
\begin{equation}
    p(\text{false-accept in third try}) = (1 - 0.005) \times (1 - 0.005)
    \times 0.005 = 0.004950
\end{equation}
Lets go straight into the fifth try.
\begin{equation}
    p(\text{false-accept in fifth try}) = (1 - 0.005)^4 \times 0.005 = 0.00490074
\end{equation}
So all of these probabilities can happen which means we can sum them up.
Sum of all these probabilities is higher than the $(0.0490074 \times 5)$ because
all of them are around the same value just some 0.0001 factors short of 0.005.
\\
So we can conclude that the probability is equal to 0.02450.
Which is around 2\% which is very high for this kind of application.
Either the admins must find another way to decrease the false-positive rates
which are very dangerous or resort to the simple password authentication or
RFID tag method that decreases the chances of false-positive compared to the
biometric ones.
\section{Q4}
\subsection{a}
\begin{enumerate}
    \item A sends it's identity and nonce to the B believing B recieved them. \\\
        B thinks it recieved nonce from A because of the recieved identity.
    \item B sends the nonce and a session key back to A. \\
        B thinks that they shared $K^\prime_{AB}$ with A because of the sent
        identity and the encrypted key $K_{AB}$ that is shared only with A
        and B.
    \item A thinks that $K^\prime_{AB}$ is fresh because it got the nonce back. \\
        A also thinks that the session key is from B because it got encrypted
        using the shared key between A and B. \\
        B thinks the key is fresh because the negotiated key and the nonce got
        back using the same shared key.
\end{enumerate}
\subsection{b}
If there is no way to find out the $K_{AB}$ there will be no ways to
understand the encrypted messages. But we can do DoS attacks to deny A and B of
their communications
\begin{enumerate}
    \item C sends the step one of this protocol to A. C knows the nonce.
    \item C copies the message of B in the step 2.
    \item C sends the message back.
\end{enumerate}
This forces the parties to create two session keys that are not the same.
Therefore the second session key will be different with the first.
So the messages will be unreadable.
\subsection{c}
B should also supply a unique nonce in the message in the step two.
This ensures that the message is only recieved by A.
\section{Q5}
\subsection{a}
A very similar situation has been described in the stallings book. \\
This scenario assumes that a master key is shared with KDC before hand.
\begin{enumerate}
    \item A asks KDC to protect a connection to B and provide a session key.
        Identitiy of A and B with a nonce is included in the message.
    \item KDC responds with a message encrypted by $K_a$. This message includes
        a session key and the original message sent by A and a message
        encrypted using the key $K_b$ intended for B that includes session key
        and the Identity of A.
    \item A sends the message generated by KDC that was encrypted using $K_b$.
        This informs B of the identity of A and session key.
    \item B sends another nonce to A using $K_s$.
    \item A uses a function on the nonce and returns it to B using a message that was
        encrypted by $K_s$.
\end{enumerate}
\subsection{b}
An attacker can slip into the steps 3 and 4 and do a replay attack and
subsitutes A. In this attack A can be thrown out of the communication.
\subsection{c}
In step 3 A should send another nonce different from the other nonces in system
to the B.
\section{Q6}
Starting with the first step of the protocol:
\begin{enumerate}
    \item Because of the preshared key: \\
        B sees $N_a$ and B believes that
        $A \stackrel{K_{ab}}{\longleftrightarrow} B$. Therefore B Believes A Said
        $(N_a, A \stackrel{K_{ab}}{\longleftrightarrow} B)$. \\
        B believes A said $(N_a, A \stackrel{K_{ab}}{\longleftrightarrow} B)$. \\
        A believes $(N_a \text{ is fresh})$ Therefore: \\
        B believes A believes $(N_a, A \stackrel{K_{ab}}{\longleftrightarrow} B)$ and
        B believes $N_a$ is fresh.
    \item A and B Believe $N_b$ is fresh because of the preshared key and 
        predefined ban logic.
    \item A sees $(N_a, N_b, A \stackrel{K_{ab}}{\longleftrightarrow} B)$
        A believes $(A \stackrel{K_{ab}}{\longleftrightarrow} B)$ \\
        B believes $(N_a is fresh, N_b is fresh)$
    \item A sees $(A \stackrel{K_{ab}^{\prime}}{\longleftrightarrow} B,
        N^{\prime}_{b})$ \\
        A believes B said $(A \stackrel{K_{ab}^{\prime}}{\longleftrightarrow} B,
        N_{b}^{\prime})$ \\
        B believes $(A \stackrel{K_{ab}^{\prime}}{\longleftrightarrow} B)$
    \item A believes B said $(A \stackrel{K_{ab}^{\prime}}{\longleftrightarrow} B)$
        A believes B believes $(A \stackrel{K_{ab}^{\prime}}{\longleftrightarrow} B, N_{a}^{\prime})$ \\
    \item Therefore A Believes $(A \stackrel{K_{ab}^{\prime}}{\longleftrightarrow} B)$
\end{enumerate}
This proves the assumptions using a series of BAN logic language literals.
So the goals are proved and using four nonces in this logic makes it really
hard to propose an attack on this protocol. Also the BAN logic language
literals prove systematically that this protocol is correct and formally
proves it.
\end{document}
