\documentclass[a4paper, 11pt]{article}
\usepackage[top=2cm, bottom=3cm, left = 2cm, right = 2cm]{geometry} 
\geometry{a4paper} 
\usepackage{textcomp}
\usepackage{graphicx} 
\usepackage{amsmath,amssymb}  
\usepackage{bm}  
\usepackage{memhfixc} 
\usepackage{fancyhdr}
\usepackage{enumerate}
\usepackage{xcolor}
\usepackage{xepersian}
\settextfont[Scale=1]{HM FNazli}
\setlatintextfont[Scale=.9]{Noto Sans}
\pagestyle{fancy}
\setlength{\headheight}{14pt}
\addtolength{\topmargin}{-2pt}

\title{
    تمرین شماره پنج
}
\author{حسین افکار}
%\date{}

\begin{document}
\maketitle
% \tableofcontents
در این بخش سعی ما بر این است که نتیجه‌گیری و عنوان مقاله را نقد کنیم.
\section{نقد نتیجه‌گیری مقاله}
در اولین بخش در مورد هدف اصلی این مقاله صحبت شده است.
\begin{latin}
We have presented MemGuard, a memory bandwidth reservation system,
for supporting efficient memory performance
isolation on multi-core platforms.
\end{latin}
بخش بعدی خلاصه مهم‌ترین یافته مقاله است که ابزار
\lr{MemGuard}
می‌باشد.
\begin{latin}
It decomposes memory
bandwidth as two parts, guaranteed bandwidth and best effort
bandwidth. Memory bandwidth reservation is provided for
the guaranteed part for achieving performance isolation. An
efficient reclaiming mechanism is proposed for effectively
utilizing the guaranteed bandwidth. It further improves system
throughput by exploiting best effort bandwidth after each core
satisfies its guaranteed bandwidth. It has been implemented
in Linux kernel and evaluated on a real multi-core hardware
platform.
\end{latin}
در آخر به شرح و بحث و توضیح راجع‌به نتایج می‌پردازد.
\begin{latin}
Our evaluation with SPEC2006 benchmarks showed that
MemGuard is able to provide memory performance isolation
under heavy memory intensive workloads on multi-core platforms.
It also showed that the proposed reclaiming algorithm
improves overall throughput compared to a reservation only
system under time-varying memory workloads.
\end{latin}
این مقاله بخش‌های محدودیت مطالعه، نتایج ضمنی مطالعه، و تحقیقات آتی را ندارد.
\section{نقد عنوان مقاله}
\begin{latin}
MemGuard: \textcolor{olive}{Memory Bandwidth Reservation
System} \textcolor{green}{for Efficient Performance Isolation} in
\textcolor{blue}{Multi-core Platforms}
\end{latin}
در عنوان مقاله بخش ویژگی حذف شده است و روش‌کار در عنوان مقاله آورده نشده است.
\bibliographystyle{abbrv}
% \bibliography{references}  % need to put bibtex references in references.bib 
\end{document}
